19Q2

### 2019-11-25 19Q2.Rmd
CN/GE Spearman corr fxn, ran corr lineage agnostic and lineage specific

```{r}
MakeDrugscreenSpearmanCorrDF <- function(dataset, df, metric, lineage) {
  df_filt <- filter(df, Drug %in% g2p_drugs & Gene %in% g2p_genes)
  df_filt$Gene <- factor(df_filt$Gene, ordered = FALSE)
  df_filt <- unfactorize(df_filt)

  if(metric == "GE") {
    if(lineage) {
      res <- df_filt %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>% drop_na(TPM) %>%
        summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
                  GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value, 
                  GE_p_log10 = -log10(GE_p))
      res$InG2P <- ifelse(res$Drug_Gene_Lin %in% unique(as.character(g2p_expr$Drug_Gene_Lin[!is.na(g2p_expr$Drug_Gene_Lin)])),   "Yes", "No")
    }
    if(!lineage) {
      res <- df_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
        summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
                  GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value, 
                  GE_p_log10 = -log10(GE_p))
      res$InG2P <- ifelse(res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])),   "Yes", "No")
    }
  }
  if(metric == "CN") {
    if(lineage) {
      res <- df_filt %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>% drop_na(CN) %>%
        summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
                  CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value,
                  CN_p_log10 = -log10(CN_p))
      res$InG2P <- ifelse(res$Drug_Gene_Lin %in% unique(as.character(g2p_amp$Drug_Gene_Lin[!is.na(g2p_amp$Drug_Gene_Lin)])), "Yes", "No")
    }
    if(!lineage) {
      res <- df_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
        summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
                  CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value, 
                  CN_p_log10 = -log10(GE_p))
      res$InG2P <- ifelse(res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])),   "Yes", "No")
    }
  }
  res$Dataset <- dataset
  return(res)
}
```

@@

```{r spear_calc, warning=FALSE, eval=FALSE}
# CRISPR
crispr_spear_cn <- crispr %>% group_by(Gene, disease) %>% drop_na(CN) %>%
  summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
            CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value,
            CN_p_log10 = -log10(CN_p),
            InG2P = "No",
            Dataset = "CRISPR",
            Metric = "Copy Number")
crispr_spear_cn <- transform(crispr_spear_cn, Gene = reorder(Gene, CN_r))
crispr_spear_cn <- add_column(crispr_spear_cn, Drug = "CRISPR", .before = "Gene")
Drug_Gene <- with(crispr_spear_cn, paste0(Drug, "_", Gene))
crispr_spear_cn <- add_column(crispr_spear_cn, Drug_Gene = Drug_Gene, .before = "Drug")
crispr_spear_cn <- add_column(crispr_spear_cn, Drug_Gene_Lin = paste0(Drug_Gene, "_", disease), .before = "Drug")
saveRDS(crispr_spear_cn, "./data_munging/rds/crispr_cn_cor_lineage.rds")

crispr_spear_ge <- crispr %>% group_by(Gene, disease) %>% drop_na(TPM) %>%
  summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
            GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
            GE_p_log10 = -log10(GE_p),
            InG2P = "No",
            Dataset = "CRISPR",
            Metric = "Gene Expression")
crispr_spear_ge <- transform(crispr_spear_ge, Gene = reorder(Gene, GE_r))
crispr_spear_ge <- add_column(crispr_spear_ge, Drug = "CRISPR", .before = "Gene")
Drug_Gene <- with(crispr_spear_ge, paste0(Drug, "_", Gene))
crispr_spear_ge <- add_column(crispr_spear_ge, Drug_Gene = Drug_Gene, .before = "Drug")
crispr_spear_ge <- add_column(crispr_spear_ge, Drug_Gene_Lin = paste0(Drug_Gene, "_", disease), .before = "Drug")
saveRDS(crispr_spear_ge, "./data_munging/rds/crispr_ge_cor_lineage.rds")

ccle_cn_res <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "CN", lineage = FALSE)
ctrp_cn_res <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "CN", lineage = FALSE)
gdsc_cn_res <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "CN", lineage = FALSE)
cn_cor <- rbind(ccle_cn_res, ctrp_cn_res, gdsc_cn_res)
saveRDS(cn_cor, "./data_munging/rds/drug_cn_cor.rds")

ccle_ge_res <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "GE", lineage = FALSE)
ctrp_ge_res <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "GE", lineage = FALSE)
gdsc_ge_res <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "GE", lineage = FALSE)
ge_cor <- rbind(ccle_ge_res, ctrp_ge_res, gdsc_ge_res)
saveRDS(ge_cor, "./data_munging/rds/drug_ge_cor.rds")
```

@@

```{r spear_calc_lin, eval=FALSE}
# CRISPR
# crispr_spear_cn <- crispr %>% group_by(Gene) %>% drop_na(CN) %>%
#   summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
#             CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value,
#             CN_p_log10 = -log10(CN_p),
#             InG2P = "No",
#             Dataset = "CRISPR",
#             Metric = "Copy Number")
# crispr_spear_cn <- transform(crispr_spear_cn, Gene = reorder(Gene, CN_r))
# crispr_spear_cn <- add_column(crispr_spear_cn, Drug = "CRISPR", .before = "Gene")
# Drug_Gene <- with(crispr_spear_cn, paste0(Drug, "_", Gene))
# crispr_spear_cn <- add_column(crispr_spear_cn, Drug_Gene = Drug_Gene, .before = "Drug")
# saveRDS(crispr_spear_cn, "./data_munging/rds/crispr_cn_cor.rds")
# 
# crispr_spear_ge <- crispr %>% group_by(Gene) %>% drop_na(TPM) %>%
#   summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
#             GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
#             GE_p_log10 = -log10(GE_p),
#             InG2P = "No",
#             Dataset = "CRISPR",
#             Metric = "Gene Expression")
# crispr_spear_ge <- transform(crispr_spear_ge, Gene = reorder(Gene, GE_r))
# crispr_spear_ge <- add_column(crispr_spear_ge, Drug = "CRISPR", .before = "Gene")
# Drug_Gene <- with(crispr_spear_ge, paste0(Drug, "_", Gene))
# crispr_spear_ge <- add_column(crispr_spear_ge, Drug_Gene = Drug_Gene, .before = "Drug")
# saveRDS(crispr_spear_ge, "./data_munging/rds/crispr_ge_cor.rds")

ccle_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "CN", lineage = TRUE)
ctrp_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "CN", lineage = TRUE)
gdsc_cn_res_lin <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "CN", lineage = TRUE)
cn_cor_lin <- rbind(ccle_cn_res_lin, ctrp_cn_res_lin, gdsc_cn_res_lin)
saveRDS(cn_cor_lin, "./data_munging/rds/drug_cn_cor_lineage.rds")

ccle_ge_res_lin <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "GE", lineage = TRUE)
ctrp_ge_res_lin <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "GE", lineage = TRUE)
gdsc_ge_res_lin <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "GE", lineage = TRUE)
ge_cor_lin <- rbind(ccle_ge_res_lin, ctrp_ge_res_lin, gdsc_ge_res_lin)
saveRDS(ge_cor_lin, "./data_munging/rds/drug_ge_cor_lineage.rds")
```

>>>>

```{r}
MakeSpearmanCorrDF <- function(dataset, df, metric, lineage) {
  df$Gene <- factor(df$Gene, ordered = FALSE)
  df <- unfactorize(df)

  if(metric == "GE") {
    if(lineage) {
      df_count <- df %>% drop_na(TPM) %>% count(Drug, Gene, disease, Drug_Gene_Lin) %>% filter(n >= 3)
      df <- filter(df, Drug_Gene_Lin %in% df_count$Drug_Gene_Lin)
      res <- df %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>%
        summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
                  GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, 
                  GE_p_log10 = -log10(GE_p))
      res$InG2P <- ifelse(res$Drug_Gene_Lin %in% unique(as.character(g2p_expr$Drug_Gene_Lin[!is.na(g2p_expr$Drug_Gene_Lin)])),   "Yes", "No")
    }
    if(!lineage) {
      res <- df %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
        summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
                  GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, 
                  GE_p_log10 = -log10(GE_p))
      res$InG2P <- ifelse(res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])),   "Yes", "No")
    }
  }
  if(metric == "CN") {
    if(lineage) {
      df_count <- df %>% drop_na(CN) %>% count(Drug, Gene, disease, Drug_Gene_Lin) %>% filter(n >= 3)
      df <- filter(df, Drug_Gene_Lin %in% df_count$Drug_Gene_Lin)
      res <- df %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>%
        summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
                  CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value,
                  CN_p_log10 = -log10(CN_p))
      res$InG2P <- ifelse(res$Drug_Gene_Lin %in% unique(as.character(g2p_amp$Drug_Gene_Lin[!is.na(g2p_amp$Drug_Gene_Lin)])), "Yes", "No")
    }
    if(!lineage) {
      res <- df %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
        summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
                  CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, 
                  CN_p_log10 = -log10(CN_p))
      res$InG2P <- ifelse(res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])),   "Yes", "No")
    }
  }
  res$Metric <- metric
  res$Dataset <- dataset
  return(res)
}
```

@@

```{r spear_calc, warning=FALSE, eval=FALSE}
# Ran this chunk on 11/25
crispr_cn_res <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "CN", lineage = FALSE)
ccle_cn_res <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "CN", lineage = FALSE)
ctrp_cn_res <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "CN", lineage = FALSE)
gdsc_cn_res <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "CN", lineage = FALSE)
cn_cor <- rbind(crispr_spear_cn, ccle_cn_res, ctrp_cn_res, gdsc_cn_res)
saveRDS(cn_cor, "./data_munging/rds/cn_cor.rds")

crispr_ge_res <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "GE", lineage = FALSE)
ccle_ge_res <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "GE", lineage = FALSE)
ctrp_ge_res <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "GE", lineage = FALSE)
gdsc_ge_res <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "GE", lineage = FALSE)
ge_cor <- rbind(crispr_ge_res, ccle_ge_res, ctrp_ge_res, gdsc_ge_res)
saveRDS(ge_cor, "./data_munging/rds/ge_cor.rds")
```

@@

```{r spear_calc_lin, eval=FALSE}
crispr_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "CN", lineage = TRUE)
ccle_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "CN", lineage = TRUE)
ctrp_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "CN", lineage = TRUE)
gdsc_cn_res_lin <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "CN", lineage = TRUE)
cn_cor_lin <- rbind(crispr_cn_res_lin, ccle_cn_res_lin, ctrp_cn_res_lin, gdsc_cn_res_lin) %>% filter(CN_p_log10 == Inf)
saveRDS(cn_cor_lin, "./data_munging/rds/cn_cor_lineage.rds")

crispr_ge_res <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "GE", lineage = TRUE)
ccle_ge_res_lin <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "GE", lineage = TRUE)
ctrp_ge_res_lin <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "GE", lineage = TRUE)
gdsc_ge_res_lin <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "GE", lineage = TRUE)
ge_cor_lin <- rbind(crispr_ge_res, ccle_ge_res_lin, ctrp_ge_res_lin, gdsc_ge_res_lin) %>% filter(GE_p_log10 == Inf)
saveRDS(ge_cor_lin, "./data_munging/rds/ge_cor_lineage.rds")
```
